Tropical Mathematics for the Lambda Calculus

### 2023-01-19 section4.tex
commit

\begin{theorem}\label{thm:cont}
 Any tropical Laurent series $f:\Lawv^X\to\Lawv$ is continuous on $\BB R_{>0}^X$, w.r.t.\ to the norm $\norm{\cdot}_\infty$.
\end{theorem}
\begin{proof}
 It follows after adaptating [Theorem , \cite{}] in order to prove that if a real-valued function on a locally convex topological $\BB R$-vector space is, locally around $x$, concave and bounded by a finite constant, then it is continuous at $x$.
\end{proof}

We conclude this subsection by noticing that $\Lawv^X$ with the usual $+$ and the usual $\cdot$ is a $\BB R_{\geq0}$-semimodule.
Together with the norm $\norm{\cdot}_\infty$, it can be proved that it is a Scott-complete \emph{normed cone} %(see~\cite{Selinger2004}, or the appendix, for such notions}.
Its cone structure induces an order on it, called its \emph{cone order}:
$x\leq y$ iff $y=x+z$ for some (unique) $z\in\Lawv^X$.
This makes it a Scott-continuous dcpo.
Suitable categories of cones have been recently investigated as models of probabilistic computation %(\cite{Crubillie2018, EhrPagTas2018, Ehrhard2020}).
We will just show that:

>>>>

\begin{theorem}\label{thm:cont}
 Any tropical Laurent series $f:\Lawv^X\to\Lawv$ is continuous on $\BB R_{>0}^X$, w.r.t.\ to the norm $\norm{\cdot}_\infty$.
\end{theorem}
\begin{proof}
 It follows after adapting [Theorem , \cite{}] in order to prove that if a real-valued function on a locally convex topological $\BB R$-vector space is, locally around $x$, concave and bounded by a finite constant, then it is continuous at $x$.
\end{proof}

We conclude this subsection by noticing that $\Lawv^X$ with the usual $+$ and the usual $\cdot$ is a $\BB R_{\geq0}$-semimodule.
Together with the norm $\norm{\cdot}_\infty$, it can be proved that it is a Scott-complete \emph{normed cone} (see~\cite{Selinger2004}, or the appendix, for such notions).
Its cone structure induces an order on it, called its \emph{cone order}:
$x\leq y$ iff $y=x+z$ for some (unique) $z\in\Lawv^X$.
This makes it a Scott-continuous dcpo.
Suitable categories of cones have been recently investigated as models of probabilistic computation (\cite{Crubillie2018, EhrPagTas2018, Ehrhard2020}).
We will just show that:
